{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-06-29 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
xx
jia you

A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, in spite of different community detection methods and various forms of social and physical human interactions were used. 
The general consensus is that the derived cohesive geographic divisions

In spite of different community with different forms of human interaction, 
However, there

The notion of distance decay has a close relationship with The First Law of Geography: ‘everything is
related to everything else, but near things are more related than distant things’ (Tobler
1970, p. 236). Although highly developed urban areas offer various means of transportation,
human activity remains to be restricted by a number of factors such as distance and
accessibility. 
Many researchers argue that the ‘death of distance’ hypothesis is premature even with today’s technologies (Wang et al. 2003, Rietveld and Vickerman 2004).

In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions.

actual movements of Twitter users (i.e., the reallocation in space) extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain. 
In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}.

@@

@@

>>>>

A common outcome observed from the mentioned studies is that the strongly connected urban regions in the form of communities in the network space yield geographically cohesive urban areas, in spite of different community detection methods and various forms of social and physical human interactions were used.
The general consensus is that those geographically cohesive urban areas are instances of spatial proximity effects, where the interaction strength between two urban regions decreases as the geographical distance between them increases~\citep{fotheringham1981}.
In particular, spatial proximity is closely related to Tobler's First Law of Geography: ``\textit{everything is related to everything else, but near things are more related than distant things}''~\citep{miller2004}.
While it is intuitively logical, few research efforts were further carried out to quantitatively understand how the spatial interactions shape the forms of connected urban areas (i.e., urban boundaries). One of the reason may due to the      
it is not an explicit constraints in these

In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions. 
actual movements of Twitter users (i.e., the reallocation in space) extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
We argue here that Twitter user mobility patterns provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain. 
In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}.

@@

\bibitem[\protect\citeauthoryear{Fotheringham}{1981}]{fotheringham1981}
Fotheringham, A.S., 1981. Spatial structure and distance-decay parameters. Annals of the Association of American Geographers, 71(3), pp.425-436.

@@

\bibitem[\protect\citeauthoryear{Miller}{2004}]{miller2004}
Miller, H.J., 2004. Tobler's first law and spatial analysis. Annals of the Association of American Geographers, 94(2), pp.284-289.
